SunPy - Python for Solar Physics

### 2014-08-27 2-1-Map.tex
cleaning up citation styles

The architecture of the map subpackage consists of a template map called
\texttt{GenericMap}, which is a subclass of \texttt{astropy.nddata.NDData}. 
\texttt{NDData} is a generic wrapper around a \texttt{numpy.ndarray} with a 
\texttt{meta} attribute to store metadata.
As \texttt{NDData} is currently still in development, \texttt{GenericMap} does 
not yet make full use of its capabilities, but this inheritance structure 
provides for future integration with \texttt{astropy}. In order to provide 
instrument- or detector-specific integration, \texttt{GenericMap} is designed
to be subclassed. Each subclass of \texttt{GenericMap} can register 
with the \texttt{Map} creation factory, which will then automatically return an instance
of the specific \texttt{GenericMap} subclass dependent upon the data provided. 
SunPy v0.4 has \texttt{GenericMap} specialisations for the following 
instruments: 
\textit{Yohkoh}/SXT, \textit{SOHO}/EIT and LASCO, \textit{RHESSI}, 
\textit{STEREO}/EUVI and COR, \textit{Hinode}/XRT,
\textit{PROBA2}/SWAP, \textit{SDO}/AIA and HMI, 
and \textit{IRIS} SJI (slit-jaw imager) frames.

@@

\begin{listing}[H]
\pythoncode{pycode_map1.txt}
\begin{center}
\includegraphics[width=0.8\columnwidth]{aia_map_example}
\end{center}
\caption{Example of the \texttt{AIAMap} specialisation of 
\texttt{GenericMap}. First, a map is created from an \textit{SDO}/AIA FITS file. In this case, a demonstration file contained within the SunPy repository is used. A cutout
of the full map is then created by specifying the desired solar-$x$ and solar-$y$ ranges of the plot in data coordinates (in this case, arcseconds), and then a quick-view plot is created with lines of heliographic longitude and latitude over-plotted.}
\label{code:aia_1}
\end{listing}

>>>>

The architecture of the map subpackage consists of a template map called
\texttt{GenericMap}, which is a subclass of \texttt{astropy.nddata.NDData}. 
\texttt{NDData} is a generic wrapper around a \texttt{numpy.ndarray} with a 
\texttt{meta} attribute to store metadata.
As \texttt{NDData} is currently still in development, \texttt{GenericMap} does 
not yet make full use of its capabilities, but this inheritance structure 
provides for future integration with \texttt{astropy}. In order to provide 
instrument- or detector-specific integration, \texttt{GenericMap} is designed
to be subclassed. Each subclass of \texttt{GenericMap} can register 
with the \texttt{Map} creation factory, which will then automatically return an instance
of the specific \texttt{GenericMap} subclass dependent upon the data provided. 
SunPy v0.4 has \texttt{GenericMap} specialisations for the following 
instruments:

\textit{Yohkoh}/SXT\footnote{SXT: Solar X-ray Telescope \citep{1991SoPh..136....1O, 1991SoPh..136...37T}.},
\textit{SOHO}/EIT and LASCO\footnote{SOHO: Solar and Heliospheric Observatory \citep{domingo1995}, EIT: Extreme Ultraviolet Telescope \citep{1995SoPh..162..291D} and LASCO: Large Angle Spectroscopic COronagraph \citep{1995SoPh..162..357B}.},
\textit{RHESSI}\footnote{RHESSI: Reuven Ramaty High Energy Solar Spectroscopic Image \citep{2002SoPh..210....3L}.},
\textit{STEREO}/EUVI and COR1/2\footnote{STEREO: Solar TErrestrial RElations Observatory \citep{2005AdSpR..36.1483K}, EUVI: Extreme Ultraviolet Imager \citep{2004SPIE.5171..111W} and COR1/2: CORonagraph 1/2 \citep{2002AdSpR..29.2017H}.},
\textit{Hinode}/XRT\footnote{XRT: X-Ray Telescope \citep{2007SoPh..243....3K, 2007SoPh..243...63G}.},
\textit{PROBA2}/SWAP\footnote{PROBA2: PRojects for On Board Autonomy 2 \citep{2013SoPh..286....5S}, SWAP: Sun Watcher Active Pixel \citep{2013SoPh..286...43S}.},
\textit{SDO}/AIA and HMI\footnote{HMI: Helioseismic Magnetic Imager, \citep{2012SoPh..275..207S}.}, and
\textit{IRIS}\footnote{IRIS: Interface Region Imaging Spectrograph \citep{2011SPD....42.1512L}.} SJI (slit-jaw imager) frames.

@@

\begin{listing}[H]
\pythoncode{pycode_map1.txt}
\begin{center}
\includegraphics[width=0.8\columnwidth]{aia_map_example}
\end{center}
\caption{Example of the \texttt{AIAMap} specialisation of 
\texttt{GenericMap}. The map is created from an \textit{SDO}/AIA FITS file, a cutout
of the full map is created by specifying the desired solar-$x$ and solar-$y$ ranges of the plot in data coordinates (in this case, arcseconds), and then a quick-view plot is created with lines of heliographic longitude and latitude over-plotted.}
\label{code:aia_1}
\end{listing}

### 2014-08-27 2-2-Lightcurve.tex
cleaning up citation styles

Currently, the \texttt{LightCurve} class is compatible with the
following data sources: the Geostationary Operational Environmental
Satellite (\textit{GOES}) X-ray Sensor (XRS), the \textit{Nobeyama
  Radioheliograph (NoRH)}, \textit{PROBA2} Large Yield Radiometer
(LYRA, \cite{2013SoPh..286...21D}), \textit{RHESSI},
\textit{SDO} EUV Variability Experiment (EVE\footnote{Note that only the level ``OCS'' and average
  CSV files is currently implemented -- see
  \url{http://lasp.colorado.edu/home/eve/data/}}, \citep{2012SoPh..275..115W}). \texttt{LightCurve}
also supports a number of solar summary indices - such as average
sunspot number - that are provided by the National Oceanic and
Atmospheric Administration (NOAA).  For each of these sources, a
subclass of the \texttt{LightCurve} object is initialised (e.g.,
\texttt{GOESLightCurve}) which inherits from \texttt{LightCurve}, but
allows instrument-specific functionality to be included.  Future
developments will introduce support for additional instruments and
data products, as well as implementing an interface similar to that of
\texttt{Map}.  Since there is no established standard as to how
time-series data should be stored and distributed, each SunPy
\texttt{LightCurve} object subclass provides the ability to download
its corresponding specific data format in its constructor and parse
that file type.

>>>>

Currently, the \texttt{LightCurve} class is compatible with the
following data sources: the Geostationary Operational Environmental
Satellite (\textit{GOES}) X-ray Sensor (XRS), the \textit{Nobeyama
  Radioheliograph (NoRH)}, \textit{PROBA2} Large Yield Radiometer
(LYRA, \citealt{2013SoPh..286...21D}), \textit{RHESSI},
\textit{SDO} EUV Variability Experiment\footnote{Note that only the level ``OCS'' and average
  CSV files is currently implemented -- see
  \url{http://lasp.colorado.edu/home/eve/data/}} (EVE, \citealt{2012SoPh..275..115W}). \texttt{LightCurve}
also supports a number of solar summary indices - such as average
sunspot number - that are provided by the National Oceanic and
Atmospheric Administration (NOAA).  For each of these sources, a
subclass of the \texttt{LightCurve} object is initialised (e.g.,
\texttt{GOESLightCurve}) which inherits from \texttt{LightCurve}, but
allows instrument-specific functionality to be included.  Future
developments will introduce support for additional instruments and
data products, as well as implementing an interface similar to that of
\texttt{Map}.  Since there is no established standard as to how
time-series data should be stored and distributed, each SunPy
\texttt{LightCurve} object subclass provides the ability to download
its corresponding specific data format in its constructor and parse
that file type.

### 2014-08-27 2-Data_Types.tex
cleaning up citation styles

These classes allow access to the data
and associated metadata and provide appropriate convenience functions to
enable analysis and visualisation. For each of these classes, the data is
stored in the \texttt{data} attribute, while the metadata should be stored 
in the \texttt{meta} attribute (currently, only \texttt{Map} has this feature 
fully implemented). 
% schriste - change this until all fixed
It is possible to instantiate the
data types from various
different sources: e.g., files, URLs, and arrays.  
In order to provide instrument-specific specialisation, the core SunPy classes 
make use of subclassing; e.g., \texttt{Map} has an \texttt{AIAMap} 
sub-type for data from the \textit{SDO}/AIA (Atmospheric Imaging Assembly; \cite{lemen2012}) instrument.

>>>>

These classes allow access to the data
and associated metadata and provide appropriate convenience functions to
enable analysis and visualisation. For each of these classes, the data is
stored in the \texttt{data} attribute, while the metadata should be stored 
in the \texttt{meta} attribute (currently, only \texttt{Map} has this feature 
fully implemented). 
% schriste - change this until all fixed
It is possible to instantiate the
data types from various
different sources: e.g., files, URLs, and arrays.  
In order to provide instrument-specific specialisation, the core SunPy classes 
make use of subclassing; e.g., \texttt{Map} has an \texttt{AIAMap} 
sub-type for data from the \textit{SDO}/AIA (Atmospheric Imaging Assembly; \citealt{lemen2012}) instrument.
